Manuscript Figures

### 2021-03-25 src/manuscript_figures.Rmd
disable correlation filtering - apply scaling instead

multi_omics_comb <- 'cnv_gex_meth_mut'
experiments <- grep(paste0('^TCGA-.*.', multi_omics_comb), names(LFs$pca_factors), value = T)
cl <- parallel::makeCluster(20)
parallel::clusterExport(cl, varlist = c('LFs', 'experiments', 'settings'))
cluster.stats <- do.call(rbind, sapply(simplify = F, names(LFs), function(tool) {
  message("Clustering top ",tool)
  stats <- do.call(rbind, pbapply::pbsapply(cl = cl, simplify = F, 
                                            intersect(names(LFs[[tool]]), experiments), 
                    function(experiment) {
    message(experiment)
    source(settings$utility_script)
    library(data.table)
    M <- LFs[[tool]][[experiment]]
    if(tool == 'maui_factors') {
      M <- remove_redundant_variables(M, perc = 99) 
    }

@@

M <- remove_redundant_variables(LFs$maui_factors[['pan-gastrointestinal.cnv_gex_meth_mut']], 
                                perc = 99)
y <- MSI[match(rownames(M), bcr_patient_barcode)]$MSI
M <- M[!is.na(y),]
y <- y[!is.na(y)]

@@

```{r}
# Analysis of non-small-cell lung cancer types (LUSC vs LUAD)
# reference study: https://www.nature.com/articles/s41598-020-77284-8
M <- remove_redundant_variables(LFs$maui_factors$nsclc.cnv_gex_meth_mut, perc = 99)
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project

@@

## TCGA subtype informed clusters 
## Use-case: pan-gastrointestinal cancers
require(survminer)
require(cluster)
pr <- 'pan-gastrointestinal' 
experiment <- paste0(pr, '.cnv_gex_meth_mut')
M <- remove_redundant_variables(LFs$maui_factors[[experiment]], perc = 99)
st <- tcga_subtypes[match(rownames(M), bcr_patient_barcode)]$Subtype_Selected
# find subtype specific LFs 
dt <- get_factor_specific_variables(M, st)

@@

M <- LFs$maui_factors[[experiment]]
M <- remove_redundant_variables(M, perc = 99)

clin <- process_clinical_covariates(rownames(M))
clin <- subset(clin, select = intersect(colnames(clin), clin_factors))

>>>>

multi_omics_comb <- 'cnv_gex_meth_mut'
experiments <- grep(paste0('^TCGA-.*.', multi_omics_comb), names(LFs$pca_factors), value = T)
cl <- parallel::makeCluster(20)
parallel::clusterExport(cl, varlist = c('LFs', 'experiments', 'settings'))
cluster.stats <- do.call(rbind, sapply(simplify = F, names(LFs), function(tool) {
  message("Clustering top ",tool)
  stats <- do.call(rbind, pbapply::pbsapply(cl = cl, simplify = F, 
                                            intersect(names(LFs[[tool]]), experiments), 
                    function(experiment) {
    message(experiment)
    source(settings$utility_script)
    library(data.table)
    M <- LFs[[tool]][[experiment]]
    if(tool == 'maui_factors') {
      #M <- remove_redundant_variables(M, perc = 99) 
      M <- scale(M)
    }

@@

M <- LFs$maui_factors[['pan-gastrointestinal.cnv_gex_meth_mut']]
M <- scale(M) #remove_redundant_variables(M, perc = 99)
y <- MSI[match(rownames(M), bcr_patient_barcode)]$MSI
M <- M[!is.na(y),]
y <- y[!is.na(y)]

@@

```{r}
# Analysis of non-small-cell lung cancer types (LUSC vs LUAD)
# reference study: https://www.nature.com/articles/s41598-020-77284-8
M <- LFs$maui_factors$nsclc.cnv_gex_meth_mut
M <- scale(M) #remove_redundant_variables(M, perc = 99)
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project

@@

## TCGA subtype informed clusters 
## Use-case: pan-gastrointestinal cancers
require(survminer)
require(cluster)
pr <- 'pan-gastrointestinal' 
experiment <- paste0(pr, '.cnv_gex_meth_mut')
M <- LFs$maui_factors[[experiment]]
M <- scale(M) #remove_redundant_variables(, perc = 99)
st <- tcga_subtypes[match(rownames(M), bcr_patient_barcode)]$Subtype_Selected
# find subtype specific LFs 
dt <- get_factor_specific_variables(M, st)

@@

M <- LFs$maui_factors[[experiment]]
clin <- process_clinical_covariates(rownames(M))
clin <- subset(clin, select = intersect(colnames(clin), clin_factors))
